Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-25 DGMM2025/computation.tex
Working on 3

We may choose an arbitrary projection \emph{axis} $a \in
\{1,\ldots,d\}$. Letting $\pi_a$ be the projector along this axis, we
can collect all the cells of $K$ that projects onto the same
points. Let $p \in K$. Then $\pi^{-1}_a(p)$ is a set of cells having
all the same coordinates except along coordinate $a$. This set can be ordered increasingly

>>>>

Let $(\ve_j)_{j=1,\dots}$ be the canonical basis of $\Z^d$.  We may
choose an arbitrary projection \emph{axis} $j \in
\{1,\ldots,d\}$. Letting $\pi_j$ be the projector along this axis, we
can collect all the cells of $K$ that projects onto the same
points. Let $p \in K$. Then $\pi^{-1}_j(p)$ is a set of cells having
all the same coordinates except along coordinate $j$. This set can be
ordered increasingly and stored as a list of integer intervals (see
Fig.~\ref{fig:lattice-representation} for an illustration).

A \emph{sequence of intervals} is an ordered list of intervals $L =
([a_i,b_i])_{i=1,\ldots,n}$ such that $a_i \in \Z, b_i \in \Z, b_i + 1
< a_{i+1}$, i.e., disjoint intervals with at least a missing
integer. We denote by $\mathbb{L}$ the set of sequences of
intervals. An integer $k$ belongs to $L$ iff $\exists i$ such that
$a_i \Le k \Le b_i$. For a finite set of integers, there is a unique
sequence of intervals representing it.

A \emph{lattice map along axis $j$} is a set of pairs $(q,L_q)$, with
$q \in \Z^{d-1}$ and $L_q \in \mathbb{L}$. The lattice map $M_K$
\emph{represents} $K$ when, for any point $p \in K$, the pair
$(\pi_j(p), L_{\pi_j(p)})$ exists in $M_K$ and $p_j \in L_{\pi_j(p)}$,
with $p_j$ the $j$-th coordinate of $p$, and reciprocally, $\forall
(q,L_q) \in M_K, \forall i \in L_q, q+i\ve_j \in K$.
